---
title: "PSYOP Price Forecast"
author: "Charliemarketplac "
date: "`r Sys.Date()`"
output:
  html_document:
    css: "styles.css"
    includes:
      in_header: header.html
    code_folding: hide
    toc: true
    toc_float: true
editor_options: 
  chunk_output_type: console
---

```{r, warning=FALSE, message=FALSE}
library(plotly)
library(forecast)
library(reactable)
library(dplyr)
```

# Intro

PSYOP token is a meme coin developed by ben.eth. This report forecasts price action 
using the query from cryptoedgar's dashboard: https://flipsidecrypto.xyz/crypto_edgar/q/2023-05-19-08-08-pm-fGdof5


# Data 

A snapshot of the data was downloaded and is provided as a csv in this repo.
It has HOUR, VOLUME, and PSYOP_PRICE (in USD). 

```{r}

psyop <- read.csv("psyop-swap-action.csv")
psyop <- psyop[-87, ]
psyop <- psyop[order(psyop$HOUR, decreasing = FALSE), ]
psyop$HOUR <- as.POSIXct(psyop$HOUR, tz = "UTC")
reactable(head(psyop))
```


# Plot 

```{r}
plot_ly(data = psyop, x = ~HOUR, y = ~PSYOPS_PRICE, size = ~VOLUME,
        type = "scatter", mode = "markers+lines")

```

# Forecast 

Using auto-arima to forecast the price. 

```{r}
price_arima <- auto.arima(y = psyop$PSYOPS_PRICE)
price_forecast <- forecast(price_arima, h = 48)
plot(price_forecast)
```

With this huge margin of error we surely cover future price action somewhere here over the next 48 hours. 

